### 2014-01-03 Docs/compilers/compilers.tex
multifab_volume note
more compiler notes

\begin{itemize}
\item Cray 8.0.2 compiles and runs \maestro\ fine on the interlagos/jaguarpf 
machine at OCLF.
\item Cray 8.0.7 compiles and runs \maestro\ fine on hopper (08/21/12).
\item Cray 8.2.1 and 8.2.2 seem to have issues with OpenMP on hopper (01/02/14).  Basically, in the initial divu iters, we appear to hang.  Compiling in debug mode works fine, but is slow.  This suggests that there is a compiler bug.
\end{itemize}

>>>>

\begin{itemize}
\item Cray 8.0.2 compiles and runs \maestro\ fine on the interlagos/jaguarpf 
machine at OCLF.
\item Cray 8.0.7 compiles and runs \maestro\ fine on hopper (08/21/12).

\item Cray 8.1.3, 8.2.1, and 8.2.2 seem to have issues with OpenMP on hopper 
 (01/02/14).  Basically, in the initial divu iters, we appear to hang.
 Compiling in debug mode works fine, but is slow.  This suggests that
 there is a compiler bug.

 A separate issue is that the ``volume'' reported by {\tt
 multifab\_volume()} seems to be wrong.  For a single level run, it
 should just be $\mathtt{nx} \times \mathtt{ny} \times \mathtt{nz}$,
 but the value reported is incorrect.
\end{itemize}
